# (PART\*) Module 00 {-}

# Don't Miss Module 00 {-}

```{r include = FALSE}
source("common.R")
#htmltools::tagList(rmarkdown::html_dependency_font_awesome())
library(tidyverse)
library(devtools)
library(DT)

```

```{r links, child="links.md"}
```


This overview is designed to orient you to the class as well as show you the rationale underlying them. 
Every module will follow a similar structure. I provide an overview of the topic and actionable learning goals.
Please watch the videos from this [playlist][pl-00] and work your way through the notes. 
Although the module-level playlists are embedded in the course, you can find the full-course video playlist [here][pl-all].


```{r, echo=FALSE}
library(vembedr)
# fall 2020
"https://www.youtube.com/watch?v=gMe4qSDiJfU" %>%
 embed_url() %>%
  use_align("center")
```


By the end of each module, you should be able to achieve all the learning goals outlined below. 
For this module those goals are...

<!--  https://ytplaylist-len.herokuapp.com/ -->


## Learning Goals for this Module (Chapter 0)
* Explain the structure of the course.
* Understand the rationale underlying the structure of the course.
* Explain the expectations for your section.

## To-Do List

I provide a list of tasks you'll need to do to complete the module. 
I provide this list to give the class structure. 
These tasks are broken down into three stages: explore, engage, and evaluate 
These stages are designed to be sequential. 
Complete the explore tasks first. 
Second, complete the engage tasks. 
Last, complete the evaluation.
For each stage, I will explicitly indicate whether specific tasks are required or merely, recommended.

The exploring portion of the class introduces you to the content of the module. 
It will consist of reading texts and viewing videos. 
Relative to the other two portions of the module, its more passive.

The engagement portion of the class facilitates you engaging with the material, interacting with the other members of the learning community. 
Students will complete two engagement activities. 
Most of the time, I'll provide multiple choices for the engagement portion of the module.

In order to successfully complete Module 0, please do the following:

* Explore:
  * Skim: the preface of your textbook (Optional)
  * View: the embedded videos connected to the learning goals.
* Engage:
  * Create: a brief video introducing yourself and post it on the discussion board.
  * Complete: the following survey.
* Evaluate:  



## Course Modality

This class is a flipped class. 
The online portions are asynchronous, and often contain pre-recorded videos. 
I've created a video highlighting how to be a successful asynchronous learner. 


```{r, echo=FALSE}
"https://www.youtube.com/watch?v=dc3D2tbl8G0" %>%
 embed_url() %>%
  use_align("center")
```

Much of this information comes from Northeastern University's [Tips for Taking Online Classes](https://www.northeastern.edu/graduate/blog/tips-for-taking-online-classes/)


### Productivity During Lockdown

```{r, echo=FALSE}
"https://www.youtube.com/watch?v=snAhsXyO3Ck" %>%
 embed_url() %>%
  use_align("center")
```

## Knowledge is Power

```{r, echo=FALSE}
"https://www.youtube.com/watch?v=ZbGMbdDLnyY" %>%
 embed_url() %>%
  use_align("center")
```

This brief video is covers the icebreaker I do in all of my classes. 
I encourage you to watch it. 
In it, I discuss stereotype threats and statistics anxiety.


## Meet Mason

```{r,echo=FALSE}
"https://www.youtube.com/watch?v=1IOCKxgowaQ" %>%
 embed_url() %>%
  use_align("center")
```

Mason Garrison is an assistant professor of quantitative psychology at Wake Forest University. 
She earned her PhD and MS in Quantitative Methods from Vanderbilt University, and her AB in Economics & Psychology from Washington University in St. Louis. 
Her research is an eclectic mix of behavior genetics, individual differences (e.g., personality, intelligence), and statistics.

On a more humanizing note, at the start of quarantine, Mason was fostering two feral kittens. 
They had been living behind the freshman dorms. 
She made the mistake of naming them. 
So now she has three cats...

* Tukey (namesake: [John Tukey](https://en.wikipedia.org/wiki/John_Tukey))
* Archie (namesake: [Archimedes](https://en.wikipedia.org/wiki/Archimedes))
* Annie (namesake: [Anne Anastasi](https://en.wikipedia.org/wiki/Anne_Anastasi)) 

## Website Tour

```{r, echo=FALSE}
"https://www.youtube.com/watch?v=Fq_hAQd78zo" %>%
 embed_url() %>%
 use_align("center")
```