# (PART\*) Module 00 {-}

# Don't Miss Module 00 {-}

```{r include = FALSE}
source("common.R")
#htmltools::tagList(rmarkdown::html_dependency_font_awesome())
library(tidyverse)
library(devtools)
library(DT)

```

```{r links, child="links.md"}
```

This overview is designed to orient you to the class as well as show you the rationale underlying them. Every module will follow a similar structure. First, I'll provide an overview of the topic and provide actionable learning goals. Please watch the videos from this [playlist][ds4p-pl-00] and work your way through the notes. Although the module-level playlists are embedded in the course, you can find the full-course video playlist [here][ds4p-pl-all]. In addition, you can find the slides for this module [here](https://github.com/DataScience4Psych/DataScience4Psych/blob/main/admin/pdfs/001_Introduction.pdf).


By the end of each module, you should be able to achieve all the learning goals outlined below. For this module those goals are...

<!--  https://ytplaylist-len.herokuapp.com/ -->


```{r, echo=FALSE}
library(vembedr)
embed_url("https://www.youtube.com/watch?v=HU39nOxcJYg&list=PLKrrdtYgOUYaEAnJX20Ryy4OSie375rVY") %>%
  use_align("center")
```


## Learning Goals for this Module (Chapter 0)
* Explain the structure of the course
* Understand the rationale underlying the structure of the course
* Explain the expectations for the blended and online sections

## To-Do List

I provide a list of tasks you'll need to do to complete the module. I provide this list to give the class structure. These tasks are broken down into two stages: explore and engage. These stages are designed to be sequential. Complete the explore tasks first. Second, complete the engage tasks. For each stage, I will explicitly indicate whether specific tasks are required or merely, recommended.

The exploring portion of the class introduces you to the content of the module. It will consist of reading texts and viewing videos. Relative to the other two portions of the module, its more passive.

The engagement portion of the class facilitates you engaging with the material, interacting with the other members of the learning community. Typically, students in the online section, will complete two engagement activities, while the blended section will complete one engagement activity in addition to attending the weekly in-class session. Most of the time, I'll provide multiple choices for the engagement portion of the module.

In order to successfully complete Module 0, please do the following:

* Explore:
  * Skim: the preface of your textbook (Optional)
  * View: the embedded videos connected to the learning goals.
* Engage:
  * Create: a brief video introducing yourself and post it on the discussion board.
  * Complete: the following survey.



## Course Modality

This class is a flipped class. The online portions are asynchronous, and often contain pre-recorded videos. I've created a video highlighting how to be a successful asynchronous learner. 


```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=dc3D2tbl8G0") %>%
  use_align("center")
```

Much of this information comes from Northeastern University's [Tips for Taking Online Classes](https://www.northeastern.edu/graduate/blog/tips-for-taking-online-classes/)

### Productivity During Lockdown


```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=snAhsXyO3Ck") %>%
  use_align("center")
```


## Knowledge is Power

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=ZbGMbdDLnyY") %>%
  use_align("center")
```

This brief video is covers the icebreaker I do in all of my classes. I encourage you to watch it. In it, I discuss stereotype threats and statistics anxiety.


## Meet Mason

```{r,echo=FALSE}
embed_url("https://www.youtube.com/watch?v=1IOCKxgowaQ") %>%
  use_align("center")
```

## Website Tour

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=Fq_hAQd78zo") %>%
 use_align("center")
```

