# (PART) Module 01 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
class_urls <- read.csv("./data/class_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Personality

This module introduces you to our course in Personality Psychology. 
Please watch the videos and work your way through the notes. 
**The videos start on the next page.** 
You can find the module playlist [here][pl-01]. 


## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below.

* Summarize the main objectives of personality psychology.
* Understand the concept of a basic approach (or paradigm).
* Define and distinguish between the major basic approaches to personality.
* Explain Funder's first law—that great strengths are usually great weaknesses and vice versa.
* Evaluate the concept of the One Big Theory (OBT) and explain why separate approaches to personality are needed.

## Module Materials

Remember that to succeed in this course, you should be consuming ALL of the resources in the Explore and Engage sections. Please use the learning goals to organize your notes. 
Optional materials ARE explicitly marked as optional and are located in the "Extras" subsection

### Explore
* Readings
  * Chapter 1 from the Personality Puzzle "THE STUDY OF THE PERSON" 
	  *  [Norton Ebook Link][ppch1_intro]
	  *  8th edition starts on page 2
* Videos
  * Located in the subchapters of this module
* Slidedecks
  * Located on Canvas
	
### Engage
* Activities
	  * Located on Canvas

### Evaluate
* Quiz
	* Located on Canvas

<!-- ### Extras  -->


# Lecture: What is Personality? {#whatisvideo}

This sequence of videos introduces personality psychology. 
It is approximately 45 minutes in length using this [neat webapp][ytplaylist]. Specifically,

* No of videos : 5

* Average length of video : 8 minutes, 39 seconds

* Total length of playlist : 43 minutes, 18 seconds.

## What is Personality? (01.01)

<!-- original version -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=0-UuQCMHmkk") %>%
  use_align("center")
```


## What do personality psychologists do? (01.02)
<!-- original version -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=q4byLfNoCLw") %>%
  use_align("center")
```

## Does personality really matter? (01.03.01)
<!--updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=RFCl_aPcPHA") %>%
  use_align("center")
```

[You can read the Meta Milgram Study yourself for free!](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0093927)

Haslam N, Loughnan S, Perry G (2014). Meta-Milgram: An Empirical Synthesis of the Obedience Experiments. PLoS ONE 9(4): e93927. https://doi.org/10.1371/journal.pone.0093927

### Milgram Experiment (01.03.02)

<!-- Not mine -->

```{r, echo=FALSE}
embed_url("https://youtu.be/eTX42lVDwA4") %>%
  use_align("center")
```

## How do we define personality? (01.04)

<!-- updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=olYigoNfBto") %>%
  use_align("center")
```

## Personality Paradigms (01.05)
<!-- updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=1TSq1LaAIdA") %>%
  use_align("center")
```

# Extra: What's My Personality?  {#whatisactivity}

This sequence of activities expands upon what I've introduced in the videos. Check them out!

## Big Five Inventory

Here is the link to the 538 version of the [Big Five Inventory-2 (BFI2)](https://projects.fivethirtyeight.com/personality-quiz/). 
It is 30 items (questions). 
I encourage you to read the accompanying article by [Maggie Koerth](https://twitter.com/maggiekb1) (2018): ["Most Personality Quizzes Are Junk Science. I Found One That Isn't"](https://fivethirtyeight.com/features/most-personality-quizzes-are-junk-science-i-found-one-that-isnt/).

## SAPA Project

I (Mason) think that this test battery is the best and most comprehensive personality (and individual differences) questionnaire out there. 
Get started right [here](https://www.sapa-project.org/survey/start.php)

Here's the summary straight from the test makers themselves... (source: https://www.sapa-project.org/)

"The SAPA Project is a [collaborative research](https://www.sapa-project.org/info/faq.html#collaboratory) tool for studying patterns of human behavior. Our goal is to find patterns among the vast number of ways that people differ from one another in terms of their [thoughts, feelings](https://www.sapa-project.org/info/personality.html#temperament), [interests](https://www.sapa-project.org/info/personality.html#interests), [abilities](https://www.sapa-project.org/info/personality.html#ability), desires, values, and preferences. Personality psychologists have been theorizing about these [domains](https://www.sapa-project.org/info/personality.html#personality) of differences for decades but the data you provide will help us to empirically integrate these domains into a single comprehensive framework.

The test on this site will give you feedback about your personality on two levels. First, you will receive scores on the 27 personality dimensions that were identified through statistical analyses of 300,000 SAPA participants. Then we will also give you scores on the so-called Big Five factors of personality plus an overall cognition score. Most people spend 15 to 25 minutes on the full test (you can quit in the middle if you want but the feedback won't be as accurate). The test is **entirely free** (absolutely no strings attached) and **completely anonymous** (no cookies, no tracking, nothing).

If you enjoy this test, please share it with others. The quality of our research improves with each participant, so we're grateful for your involvement!"
