# (PART) Module 01 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
class_urls <- read.csv("./data/class_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Personality

This module introduces you to our course in Personality Psychology. Please watch the videos and work your way through the notes. **The videos start on the next page.**  You can find the module playlist [here](https://www.youtube.com/playlist?list=PLKrrdtYgOUYZ2BXy4ypzoPdA39mszdnlc). Most of the slides used to make the videos in this module can be found in the [slides repo][slides]. 

## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below.

* Summarize the main objectives of personality psychology.
* Understand the concept of a basic approach (or paradigm).
* Define and distinguish between the major basic approaches to personality.
* Explain Funder's first law—that great strengths are usually great weaknesses and vice versa.
* Evaluate the concept of the One Big Theory (OBT) and explain why separate approaches to personality are needed.

## Module Materials

### Explore
* Readings
  * Chapter 1 from the Personality Puzzle "THE STUDY OF THE PERSON" 
	  *  [Norton Ebook Link](https://digital.wwnorton.com/75895/r/goto/cfi/22!/4) 
	  *  8th edition starts on page 2
* Videos
  * Located in the subchapters of this module
* Slidedecks
	* Located on Canvas
	
### Engage
* Activities
	* [Big Five Inventory-2 (BFI2)](https://projects.fivethirtyeight.com/personality-quiz/)

### Evaluate
* Quiz
	* Located on Canvas



### Estimated Video Length

<!--https://www.youtube.com/playlist?list=PLKrrdtYgOUYao_7t5ycK4KDXNKaY-ECup & https://ytplaylist-len.herokuapp.com/ -->



# What is Personality?

## What is Personality? (01.01)
<!-- original version -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=0-UuQCMHmkk") %>%
  use_align("center")
```

Here is the link to the 538 version of the [Big Five Inventory-2 (BFI2)](https://projects.fivethirtyeight.com/personality-quiz/). It is 30 items (questions). I encourage you to read the accompanying article by [Maggie Koerth](https://twitter.com/maggiekb1) (2018): ["Most Personality Quizzes Are Junk Science. I Found One That Isn't"](https://fivethirtyeight.com/features/most-personality-quizzes-are-junk-science-i-found-one-that-isnt/).

## What do personality psychologists do? (01.02)
<!-- original version -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=q4byLfNoCLw") %>%
  use_align("center")
```

## Does personality really matter? (01.03)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```

## How do we define personality? (01.04)
<!-- updated -->
```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=olYigoNfBto") %>%
  use_align("center")
```

## Personality Paradigms (01.05)
<!-- updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=1TSq1LaAIdA") %>%
  use_align("center")
```
