# (PART) Module 02 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
class_urls <- read.csv("./data/class_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Personality Methods

This module is designed to introduce you to methods of personality research. 
Please watch the videos and work your way through the notes. 
**The videos start on the next page.**  You can find the module playlist [here][pl-02].

## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below:

* Understand that personality is not directly observable, and data are clues.
* Recognize and classify instances of B, L, I, and S data.
* Define and distinguish B, L, I, and S data.
* Identify strengths and weaknesses of B, L, I, and S data.
* Understand new concepts and terminology associated with different types of data.
* Differentiate the goals of scientific training from technical training.
* Define and distinguish reliability and validity.
* Give examples of techniques researchers can use to improve measurement quality.
* Identify a variety of issues related to generalizability.
* Compare and contrast different types of research designs.


## Module Materials

### Explore
* Readings
	* Chapter 2 from the Personality Puzzle
	* Located on Canvas
* Videos
  * Located in the subchapters of this module
* Slidedecks
	* Located on Canvas

### Engage
* Activities
	* Located on Canvas

### Evaluate
* Activities
	* Located on Canvas



### Estimated Video Length

<!-- https://www.youtube.com/playlist?list=PLKrrdtYgOUYbl28Bp_qnCAuXqGT3fXlvf & https://ytplaylist-len.herokuapp.com/ -->
No of videos : 11

Average length of video : 10 minutes, 44 seconds

Total length of playlist : 1 hour, 58 minutes, 14 seconds



# Lecture: Personality Research Methods

## Roadmap for personality research (02.01)
<!-- updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=XN1GeS7FSio") %>%
  use_align("center")
```

## Self Data (02.02.01)
<!-- updated; original was two parts; this notation is here because the numbering differs across videos -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=1Bdt3v6bW2k") %>%
  use_align("center")
```

## Informant Data (02.02.02)
<!-- updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=J9bMPFLlpAc") %>%
  use_align("center")
```

## Life Outcome and Behavioral Data (02.03)

<!-- updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=TSbMg14CqRQ") %>%
  use_align("center")
```

## Data Quality (02.04)
<!-- keep original -->
```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=Py-3LjJYzKk") %>%
  use_align("center")
```

## Introducing Validity and What's a construct? (02.05)

<!-- keep original -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=MgTZUP7Dzlk") %>%
  use_align("center")
```

## Generalizability (02.06)

<!-- updated  -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=xpPlRDn4WJM") %>%
  use_align("center")
```

## Causal Inference and Generalizability in Action (02.07)

<!-- updated  -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=lLk8iWtg22A") %>%
  use_align("center")
```

## Research Designs (02.08)


<!-- updated-->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=6MKSjsPfYhc") %>%
  use_align("center")
```

## Correlational Methods (02.09)

<!-- updated-->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=6MKSjsPfYhc") %>%
  use_align("center")
```
