# (PART) Module 02 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
class_urls <- read.csv("./data/class_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Personality Methods

This module is designed to introduce you to methods of personality research. 
Please watch the videos and work your way through the notes. 
**The videos start on the next page.**  You can find the module playlist [here][pl-02].

## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below:

* Understand that personality is not directly observable, and data are clues.
* Recognize and classify instances of B, L, I, and S data.
* Define and distinguish B, L, I, and S data.
* Identify strengths and weaknesses of B, L, I, and S data.
* Understand new concepts and terminology associated with different types of data.
* Differentiate the goals of scientific training from technical training.
* Define and distinguish reliability and validity.
* Give examples of techniques researchers can use to improve measurement quality.
* Identify a variety of issues related to generalizability.
* Compare and contrast different types of research designs.


## Module Materials

### Explore
* Readings
	* Chapter 2 from the Personality Puzzle
	* Located on Canvas
* Videos
  * Located in the subchapters of this module
* Slidedecks
	* Located on Canvas

### Engage
* Activities
	* Located on Canvas

### Evaluate
* Activities
	* Located on Canvas



### Estimated Video Length

<!-- & https://ytplaylist-len.herokuapp.com/ -->



# Personality Research Methods

## Roadmap for personality research (02.01)
<!-- updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=XN1GeS7FSio") %>%
  use_align("center")
```

## Self Data (02.02)
<!-- updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=1Bdt3v6bW2k") %>%
  use_align("center")
```

## Informant Data (02.03)
<!-- updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=J9bMPFLlpAc") %>%
  use_align("center")
```

## Life Outcome and Behavioral Data (02.04)

<!-- updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=TSbMg14CqRQ") %>%
  use_align("center")
```


## Data Quality (02.04)
<!-- not yet updated -->
```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=Py-3LjJYzKk") %>%
  use_align("center")
```

## Introducing Validity and What's a construct? (02.05)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=MgTZUP7Dzlk") %>%
  use_align("center")
```

## Causal Inference and Generalizability in Action (02.06)

<!-- testing 08.02/personality 02.06 -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=dfNKuqaL-uU") %>%
  use_align("center")
```

## Research Designs (02.07)


<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=W9a71BMEajs") %>%
  use_align("center")
```
