# (PART) Module 02 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
ds4p_urls <- read.csv("./data/ds4p_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Personality Methods

This module is designed to introduce you to methods of Personality research. Please watch the videos and work your way through the notes. **The videos start on the next page.**  You can find the module playlist [here][pl-02]. Most of the slides used to make the videos in this module can be found in the [slides repo][slides]. 

## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below.

* 

## Module Materials

### Explore
* Readings
* Videos
  * Located in the subchapters of this module
* Slidedecks
### Engage
* Activities
	* Located on Canvas

### Evaluate
* Activities
	* Located on Canvas



### Estimated Video Length

<!--https://www.youtube.com/playlist?list=PLKrrdtYgOUYao_7t5ycK4KDXNKaY-ECup & https://ytplaylist-len.herokuapp.com/ -->



# Personality Research Methods

## Roadmap for personality research (02.01)
<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=02nDf5z8a_M") %>%
  use_align("center")
```

## Self and Informant Data (02.02)
<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=HS5L3bubus8") %>%
  use_align("center")
```

## Life Outcome and Behavioral Data (02.03)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=va0qMg6TTA4") %>%
  use_align("center")
```


## Data Quality (02.04)
<!-- not yet updated -->
```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=olYigoNfBto") %>%
  use_align("center")
```

## Introducing Validity and What's a construct? (02.05)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=MgTZUP7Dzlk") %>%
  use_align("center")
```

## Generalizability (02.06)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=ej8836XtNE") %>%
  use_align("center")
```

## Generalizability in Action and Research Designs (02.07)


<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=W9a71BMEajs") %>%
  use_align("center")
```
