# (PART) Module 03 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
class_urls <- read.csv("./data/class_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Personality Assessment

This module is designed to <TOPIC>. Please watch the videos and work your way through the notes. **The videos start on the next page.**  You can find the module playlist [here](https://www.youtube.com/playlist?list=PLKrrdtYgOUYZ2BXy4ypzoPdA39mszdnlc). Most of the slides used to make the videos in this module can be found in the [slides repo][slides]. 

## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below.

* Define personality assessment and key concepts associated with assessment.
* Distinguish between S and B data, as they relate to projective versus objective tests, in personality assessment.
* Understand projective tests and evaluate their merits.
* Define objective tests and recognize examples of them.
* Explain and distinguish different methods of objective test construction.
* Recognize strengths and weaknesses of different methods of objective test construction.
* Explain how factor analytic methods revealed the Big Five traits.
* Understand the process of evaluating research with significance testing.
* Illustrate the use of effect sizes as a means of evaluating research.
* Interpret and recognize important ethical issues related to personality assessment.
* Explain the principle of replication and evaluate its merit in science.
* Identify some of the possible questionable research practices and explain how they can be avoided.
* Understand the properties of and reasons behind the emergence of open science.


## Module Materials

### Explore
* Readings
	* Chapter 3 from the Personality Puzzle
	* Located on Canvas
* Videos
  * Located in the subchapters of this module
* Slidedecks
	* Located on Canvas
	
### Engage
* Activities
	* Located on Canvas
	
### Evaluate
* Quiz
	* Located on Canvas

### Extras
	* [My Psychological Testing Course](https://r-computing-lab.github.io/psychtesting/index.html)

### Estimated Video Length

<!--https://www.youtube.com/playlist?list=PLKrrdtYgOUYao_7t5ycK4KDXNKaY-ECup & https://ytplaylist-len.herokuapp.com/ -->



# What is Module?

## Video 1

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```


## Video 2

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```

## Video 3

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```
