# (PART) Module 03 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
class_urls <- read.csv("./data/class_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Personality Assessment

This module focuses on personality assessment, evaluation, and ethics. 
Please watch the videos and work your way through the notes. 
**The videos start on the next page.**  
You can find the module playlist [here][pl-03]. 

## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below.

* Define personality assessment and key concepts associated with assessment.
* Distinguish between S and B data, as they relate to projective versus objective tests, in personality assessment.
* Understand projective tests and evaluate their merits.
* Define objective tests and recognize examples of them.
* Explain and distinguish different methods of objective test construction.
* Recognize strengths and weaknesses of different methods of objective test construction.
* Explain how factor analytic methods revealed the Big Five traits.
* Understand the process of evaluating research with significance testing.
* Illustrate the use of effect sizes as a means of evaluating research.
* Interpret and recognize important ethical issues related to personality assessment.
* Explain the principle of replication and evaluate its merit in science.
* Identify some of the possible questionable research practices and explain how they can be avoided.
* Understand the properties of and reasons behind the emergence of open science.


## Module Materials

### Explore
* Readings
	* Chapter 3 from the Personality Puzzle
		* [Norton Ebook Link][ppch3_measure]
* Videos
  * Located in the subchapters of this module
* Slidedecks
	* Located on Canvas
	
### Engage
* Activities
	* Located on Canvas
	
### Evaluate
* Quiz
	* Located on Canvas

### Extras

* [My Psychological Testing Course](https://r-computing-lab.github.io/psychtesting/index.html)


# Lecture: Personality Assessment {#assessmentvideo}

This sequence of videos introduces personality assessment. It is approximately 2.25 hours in length using this [neat webapp][ytplaylist]. Specifically,

* No of videos : 9

* Average length of video : 12 minutes, 17 seconds

* Total length of playlist : 1 hour, 50 minutes, 34 seconds



## Roadmap for personality assessment (03.01)

<!-- updated -->

```{r, echo=FALSE}
"https://youtu.be/ym35piQGiGg" %>%
 embed_url() %>%
  use_align("center")
```

## Projective Tests (03.02)

<!-- updated -->

```{r, echo=FALSE}
"https://youtu.be/Po4UBLMjkwE" %>%
 embed_url() %>%
  use_align("center")
```

## Rational Objective Tests (03.03)


<!--updated -->

```{r, echo=FALSE}
"https://youtu.be/c79D9ye6u0I" %>%
 embed_url() %>%
  use_align("center")
```


## Objective Tests and Factor Analysis (03.04)


<!-- updated -->

```{r, echo=FALSE}
"https://youtu.be/kgTPg8QasEE" %>%
 embed_url() %>%
  use_align("center")
```


## Empirical Test Construction (03.05)


<!-- updated -->

```{r, echo=FALSE}
"https://youtu.be/fGpNbi63eBM" %>%
 embed_url() %>%
  use_align("center")
```

## Significance Testing (03.06)


<!-- updated -->

```{r, echo=FALSE}
"https://youtu.be/T98LVErpNmI" %>%
 embed_url() %>%
  use_align("center")
```

```{r, echo=FALSE}
try(include_tweet("https://twitter.com/MaartenvSmeden/status/1434619122189545472"))
```

## Effect Size (03.07)


<!-- updated -->

```{r, echo=FALSE}
"https://youtu.be/z3BJ-MrITeQ" %>%
 embed_url() %>%
  use_align("center")
```



## Personality Testing Ethics (03.08)


<!-- updated -->

```{r, echo=FALSE}
"https://youtu.be/PVVNL5Zs1tc" %>%
 embed_url() %>%
  use_align("center")
```

## More problems (03.09)
<!-- updated -->

```{r, echo=FALSE}
"https://youtu.be/JouO7-iLVpc" %>%
 embed_url() %>%
  use_align("center")
```
