# (PART) Module 04 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
class_urls <- read.csv("./data/class_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Persons and Situations

This module is introduces the trait approach within the context of the person versus situation debate. 
Please watch the videos and work your way through the notes. 
**The videos start on the next page.** 
You can find the module playlist [here][pl-04]. 

## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below.

* Recognize features of the trait approach.
* Understand and apply the concepts of cross-situational consistency and stability.
* Recall the proponents (and their arguments) in the person-situation debate.
* Explain the situationist position.
* Understand and give evidence for the pro-personality response.
* Distinguish the situationist critique from the personality response.
* Use correlational effect sizes to compare the predictive power of person and situation.
* Understand that people are both consistent and change.
* Recognize different life outcomes that are associated with different traits.
* Identify and generate examples of the principle of interactionism.
* Evaluate how values might influence people to support a situationist or pro-personality position.


## Module Materials

### Explore
* Readings
	* Chapter 4 from the Personality Puzzle
	  *  [Norton Ebook Link][ppch4]
* Videos
  * Located in the subchapters of this module
* Slidedecks
	* Located on Canvas
	
### Engage
* Activities
	* Located on Canvas
	
### Evaluate
* Quiz
	* Located on Canvas


# Lecture: Person vs. Situation? {#pvsvideo}

This sequence of videos introduces the person vs situation debate. 
It is approximately 60 minutes in length using this [neat webapp][ytplaylist]. Specifically,

* No of videos : 4

* Average length of video : 15 minutes, 37 seconds

* Total length of playlist : 1 hour, 2 minutes, 31 seconds

## Person vs Situation (04.01)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=A1MPuEiphJ4") %>%
  use_align("center")
```


## Extra Context about the Person Versus Situation Debate (04.02)
<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=LyuIfx2ft-w") %>%
  use_align("center")
```

## What's this debate anyway? (04.03)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=BGX6csdSgvE") %>%
  use_align("center")
```

## Personality and Life (04.04)

<!-- keep -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=eKb-HONj-Ds") %>%
  use_align("center")
```
