# (PART) Module 05 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
class_urls <- read.csv("./data/class_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Personality Judgment and the Self

This module is designed to <TOPIC>. Please watch the videos and work your way through the notes. **The videos start on the next page.**  You can find the module playlist [here](https://www.youtube.com/playlist?list=PLKrrdtYgOUYZ2BXy4ypzoPdA39mszdnlc). Most of the slides used to make the videos in this module can be found in the [slides repo][slides]. 

## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below.

### Chapter 5:
* Recognize that people judge themselves and others, and these judgments have consequences.
* Understand the concept of expectancy effect and the self-fulfilling prophecy.
* Summarize how the accuracy of personality judgment is assessed.
* Differentiate between the constructivist and critical realist positions.
* Give examples of the accuracy of first impressions.
* Understand the four variables that affect the likelihood of accurate personality judgment.
* Differentiate between the different stages of the Realistic Accuracy Model.
* Evaluate the difficulties in creating accurate personality judgments.
* Understand the circumstances around high and low accuracy of self-knowledge.
* Describe the ways in which one can improve self-knowledge.
### Chapter 15:
* Understand the distinction between the I and the me and the function of each.
* Be able to identify the types of self-knowledge (e.g., self-schema, self-esteem, and self-efficacy) that are associated with the declarative self and know how they are measured and what their implications are.
* Understand the inner workings of memory and how it is related to the establishment of one’s self-concept.
* Be able to explain how one can have “possible selves,” the discrepancy between different “selves,” and the controversy around this idea.
* Understand the central tenets of the procedural knowledge and declarative knowledge and how they are distinct from one an-other.
* Distinguish between relational selves and implicit selves.
* Discuss psychotherapeutic and layperson strategies to change procedural knowledge.
* Understand the ideas behind a working self-concept and how it relates to declarative and procedural knowledge.
* Understand the concept of self-esteem and how it relates to the self.
* Understand how procedural knowledge can be assessed.

## Module Materials

### Explore
* Readings
	* Chapter 5 and 15 from the Personality Puzzle
	* Located on Canvas
* Videos
  * Located in the subchapters of this module
* Slidedecks
	* Located on Canvas
	
### Engage
* Activities
	* Located on Canvas
	
### Evaluate
* Quiz
	* Located on Canvas



### Estimated Video Length

<!--https://www.youtube.com/playlist?list=PLKrrdtYgOUYao_7t5ycK4KDXNKaY-ECup & https://ytplaylist-len.herokuapp.com/ -->



# What is Module?

## Video 1

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```


## Video 2

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```

## Video 3

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```
