# (PART) Module 06 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
class_urls <- read.csv("./data/class_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Trait Theory

This module introduces expands upon trait theory. Please watch the videos and work your way through the notes. **The videos start on the next page.**  You can find the module playlist [here](https://www.youtube.com/playlist?list=PLKrrdtYgOUYZ2BXy4ypzoPdA39mszdnlc). 

## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below.

* Distinguish between the four different approaches to studying traits.
* Understand self-monitoring and narcissism as exemplars of the single-trait approach.
* Explain and recognize examples of the many-trait approach.
* Understand the theoretical approach to uncovering essential traits.
* Recognize theorists and practices associated with the essential-trait approach.
* Recognize and classify outcomes and facets associated with traits in the Big Five framework.
* Explain limitations to the typological approach to personality traits.
* Summarize the factor analytic approach to uncovering essential traits.
* Understand both the applications and criticisms of the Myers-Briggs Type Indicator.
* Explain the function and usefulness of personality types.


## Module Materials

### Explore
* Readings
	* Chapter 6 from the Personality Puzzle
	* Located on Canvas
* Videos
  * Located in the subchapters of this module
* Slidedecks
	* Located on Canvas
	
### Engage
* Activities
	* Located on Canvas
	
### Evaluate
* Quiz
	* Located on Canvas



### Estimated Video Length

<!--https://www.youtube.com/playlist?list=PLKrrdtYgOUYao_7t5ycK4KDXNKaY-ECup & https://ytplaylist-len.herokuapp.com/ -->



# Lecture: What is Trait Theory?

## Personality Traits Roadmap (06.01)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=ukxPyA223cc") %>%
  use_align("center")
```


## The Single- and Multi-Trait Approaches (06.02)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=2xBoyrhBh3I") %>%
  use_align("center")
```

## The Psychology of Narcissim (06.02b)

<!-- updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=arJLy3hX1E8") %>%
  use_align("center")
```


## The Essential Trait Approach (06.03)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=bdERzNy0XAA") %>%
  use_align("center")
```

## Big 5 Factors (06.04)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=YyNHU5DP1Fk") %>%
  use_align("center")
```

## Personality Types (06.05)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=zzSdhlfbupc") %>%
  use_align("center")
```
