# (PART) Module 06 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
class_urls <- read.csv("./data/class_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Personality Stability, Development, and Change

This module covers personality stability, development, and change. Please watch the videos and work your way through the notes. **The videos start on the next page.**  You can find the module playlist [here][pl-06]

## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below.

* Describe how personality remains stable over the life course in terms of rank-order consistency.
* Explain how personality changes over the life span in terms of its trends and specific causes.
* Identify the basic tenets of Developmental Personality Psychology.
* Relate personality change to both psychotherapeutic interventions and layperson strategies for personal change.
* Identify and describe the ways in which personality development is studied in psychology.
* Distinguish between the seven principles of personality continuity and change.
* Identify the ways in which early life experiences and childhood temperament contribute to the trajectory of one's personality trait structure development.
* Describe how research conducted over the last 40 years has contributed to our understanding of both personality change and stability.
* Explain the ways in which individuals develop their goals and narrative identity.
* Discuss the negative consequences for both personality stability and personality change.
 


## Module Materials

### Explore
* Readings
	* Located on Canvas
	* Chapter 7 from the Personality Puzzle
* Videos
  * Located in the subchapters of this module
* Slidedecks
	* Located on Canvas
	
### Engage
* Activities
	* Located on Canvas
	
### Evaluate
* Quiz
	* Located on Canvas



### Estimated Video Length

<!--https://www.youtube.com/playlist?list=PLKrrdtYgOUYao_7t5ycK4KDXNKaY-ECup & https://ytplaylist-len.herokuapp.com/ -->



# Lecture: Personality over Time

## Personality over the Lifespan (06.01)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=b_j5BSXFRx4") %>%
  use_align("center")
```


## Personality Stability (06.02)


<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=D_AnB53MQ94") %>%
  use_align("center")
```

## Personality Development (06.03)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=Ervcry6uqHQ") %>%
  use_align("center")
```

## Personality Change (06.04)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=ZIJooF8YxHA") %>%
  use_align("center")
```

## Narrative Identity (06.05)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://youtu.be/yz7nzur5EhA") %>%
  use_align("center")
```

## Dan P. McAdams at TEDxHendrixCollege: “In the Beginning” and “Once upon a Time” (06.06)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://youtu.be/uxB3gSnMiNw") %>%
  use_align("center")
```
