# (PART) Module 07 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
class_urls <- read.csv("./data/class_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Personality Stability, Development, and Change

This module is designed to <TOPIC>. Please watch the videos and work your way through the notes. **The videos start on the next page.**  You can find the module playlist [here](https://www.youtube.com/playlist?list=PLKrrdtYgOUYZ2BXy4ypzoPdA39mszdnlc). 

## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below.

* Describe how personality remains stable over the life course in terms of rank-order consistency.
* Explain how personality changes over the life span in terms of its trends and specific causes.
* Identify the basic tenets of Developmental Personality Psychology.
* Relate personality change to both psychotherapeutic interventions and layperson strategies for personal change.
* Identify and describe the ways in which personality development is studied in psychology.
* Distinguish between the seven principles of personality continuity and change.
* Identify the ways in which early life experiences and childhood temperament contribute to the trajectory of one's personality trait structure development.
* Describe how research conducted over the last 40 years has contributed to our understanding of both personality change and stability.
* Explain the ways in which individuals develop their goals and narrative identity.
* Discuss the negative consequences for both personality stability and personality change.
 


## Module Materials

### Explore
* Readings
	* Located on Canvas
	* Chapter 7 from the Personality Puzzle
* Videos
  * Located in the subchapters of this module
* Slidedecks
	* Located on Canvas
	
### Engage
* Activities
	* Located on Canvas
	
### Evaluate
* Quiz
	* Located on Canvas



### Estimated Video Length

<!--https://www.youtube.com/playlist?list=PLKrrdtYgOUYao_7t5ycK4KDXNKaY-ECup & https://ytplaylist-len.herokuapp.com/ -->



# What is Module?

## Video 1

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```


## Video 2

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```

## Video 3

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```
