# (PART) Module 08 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
class_urls <- read.csv("./data/class_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Anatomy and Physiology of Personality

This module is designed to <TOPIC>. Please watch the videos and work your way through the notes. **The videos start on the next page.**  You can find the module playlist [here](https://www.youtube.com/playlist?list=PLKrrdtYgOUYZ2BXy4ypzoPdA39mszdnlc). 

## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below.

*  Understand how psychologists and biologists tried to explain the mind-body problem over the years.
*  Define and relate the parts of the brain to their respective Big Five personality trait and emotional or behavioral outcome.
*  Define and relate neural chemicals (i.e., neurotransmitters and hormones) to their respective Big Five personality trait and emotional or behavioral outcome.
*  Recall the different parts of the neural pathways and how the brain’s chemical impulses (neurotransmitters and hormones) are directed throughout the body.
*  Understand the bidirectional cause-effect relationship between the brain, its neural chemicals, and behavior.
*  Understand the various ways to measure and assess brain activity and function in terms of what they do and why/how they were developed.
*  Recall the specific scientific outcomes for each brain activity measurement and assessment procedure (including psychosurgeries) in terms of the general benefits of each and what we learn from their results.
*  Recall the disadvantages, drawbacks, and critiques of each of the brain activity measurement and assessment procedures (including psychosurgeries).
*  Link parts of the brain with certain neurotransmitters and hormones.
*  Understand the importance of studying the brain in terms of its systems.
*  Apply behavioral outcomes of brain damage to explain the biological basis for personality and emotion.
 


## Module Materials

### Explore
* Readings
	* Located on Canvas
	* Chapter 8 from the Personality Puzzle
* Videos
  * Located in the subchapters of this module
* Slidedecks
	* Located on Canvas
	
### Engage
* Activities
	* Located on Canvas
	
### Evaluate
* Quiz
	* Located on Canvas



### Estimated Video Length

<!--https://www.youtube.com/playlist?list=PLKrrdtYgOUYao_7t5ycK4KDXNKaY-ECup & https://ytplaylist-len.herokuapp.com/ -->



# What is Module?

## Video 1

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```


## Video 2

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```

## Video 3

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```
