# (PART) Module 08 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
class_urls <- read.csv("./data/class_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Anatomy and Physiology of Personality

This module is covers Anatomy and Physiology of Personality. Please watch the videos and work your way through the notes. **The videos start on the next page.**  You can find the module playlist [here](https://www.youtube.com/playlist?list=PLKrrdtYgOUYZ2BXy4ypzoPdA39mszdnlc). 

## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below.

*  Understand how psychologists and biologists tried to explain the mind-body problem over the years.
*  Define and relate the parts of the brain to their respective Big Five personality trait and emotional or behavioral outcome.
*  Define and relate neural chemicals (i.e., neurotransmitters and hormones) to their respective Big Five personality trait and emotional or behavioral outcome.
*  Recall the different parts of the neural pathways and how the brain’s chemical impulses (neurotransmitters and hormones) are directed throughout the body.
*  Understand the bidirectional cause-effect relationship between the brain, its neural chemicals, and behavior.
*  Understand the various ways to measure and assess brain activity and function in terms of what they do and why/how they were developed.
*  Recall the specific scientific outcomes for each brain activity measurement and assessment procedure (including psychosurgeries) in terms of the general benefits of each and what we learn from their results.
*  Recall the disadvantages, drawbacks, and critiques of each of the brain activity measurement and assessment procedures (including psychosurgeries).
*  Link parts of the brain with certain neurotransmitters and hormones.
*  Understand the importance of studying the brain in terms of its systems.
*  Apply behavioral outcomes of brain damage to explain the biological basis for personality and emotion.
 


## Module Materials

### Explore
* Readings
	* Located on Canvas
	* Chapter 8 from the Personality Puzzle
* Videos
  * Located in the subchapters of this module
* Slidedecks
	* Located on Canvas
	
### Engage
* Activities
	* Located on Canvas
	
### Evaluate
* Quiz
	* Located on Canvas



### Estimated Video Length

<!--https://www.youtube.com/playlist?list=PLKrrdtYgOUYao_7t5ycK4KDXNKaY-ECup & https://ytplaylist-len.herokuapp.com/ -->



# Lecture: Biopsych and personality

## Brains! (08.01)


<!-- not yet updated -->

```{r, echo=FALSE}
"https://youtu.be/Azpleyog8m8" %>%
 embed_url() %>%
  use_align("center")
```


## Brain-Based Research Methods (08.02)


<!-- not yet updated -->

```{r, echo=FALSE}
"https://youtu.be/MiX8-f-6hjE" %>%
 embed_url() %>%
  use_align("center")
```

## Brain Parts (08.03)

<!-- not yet updated -->

```{r, echo=FALSE}
"https://youtu.be/gBymtP_A-cg" %>%
 embed_url() %>%
  use_align("center")
```

## The Frontal Lobe, Phineas Gage, and Psychosurgery (08.04)

<!-- not yet updated -->

```{r, echo=FALSE}
"https://youtu.be/xp-scBPhFMo" %>%
 embed_url() %>%
  use_align("center")
```


```{r, echo=FALSE}
try(include_tweet("https://twitter.com/JoshuaGrubbsPhD/status/1444813677815795717?s=20"))
```


## The Biochemistry of Personality (08.05)
<!-- not yet updated -->

```{r, echo=FALSE}
"https://youtu.be/95CLJbFG58Q" %>%
 embed_url() %>%
  use_align("center")
```

## Hormones! (08.06)

<!-- not yet updated -->

```{r, echo=FALSE}
"https://youtu.be/-eQ9naRibcE" %>%
 embed_url() %>%
  use_align("center")
```
