# (PART) Module 10 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
class_urls <- read.csv("./data/class_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Evolutionary Psychology

This module is introduces Evolutionary Psychology. Please watch the videos and work your way through the notes. **The videos start on the next page.**  You can find the module playlist [here](https://www.youtube.com/playlist?list=PLKrrdtYgOUYZ2BXy4ypzoPdA39mszdnlc). 

## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below.

* Identify the five stress tests (and other criticisms) and their defenses.
* Know the theoretical and historical basis for evolutionary psychological theory and how it adds to our understanding of people beyond biological sciences.
* Understand how evolutionary processes maintain individual differences.
* Be able to explain behavioral trends as evolved psychological mechanisms.
* Define sociometer and inclusive fitness.
* Explain sex differences from an evolutionary psychology perspective.
* Explain sex differences from a social theory perspective.
* Understand the current methods in the field of evolutionary psychology.
* Distinguish between biology, evolutionary psychology, and behavior genetics.

## Module Materials

### Explore
* Readings
	* Located on Canvas
	* Parts of Chapter 9 from the Personality Puzzle
* Videos
  * Located in the subchapters of this module
* Slidedecks
	* Located on Canvas
	
### Engage
* Activities
	* Located on Canvas
	
### Evaluate
* Quiz
	* Located on Canvas



### Estimated Video Length

<!--https://www.youtube.com/playlist?list=PLKrrdtYgOUYao_7t5ycK4KDXNKaY-ECup & https://ytplaylist-len.herokuapp.com/ -->



# Lecture: What is Evolutionary Psychology?

## Introduction to Evolutionary Psychology (10.01)

<!-- keep -->

```{r, echo=FALSE}
"https://youtu.be/v6DRO1z0XTY" %>%
 embed_url() %>%
  use_align("center")
```


### What is Evolution? (10.01B)

<!-- keep not mine-->

```{r, echo=FALSE}
"https://youtu.be/GhHOjC4oxh8" %>%
 embed_url() %>%
  use_align("center")
```

### What is Natural Selection? (10.01C)

<!-- keep not mine-->

```{r, echo=FALSE}
"https://youtu.be/7VM9YxmULuo" %>%
 embed_url() %>%
  use_align("center")
```




## Evolutionary Personality Psychology (10.02)

<!-- not yet updated -->

```{r, echo=FALSE}
"https://youtu.be/r0NLwkDESxI" %>%
 embed_url() %>%
  use_align("center")
```

## Individual Differences in Evolutionary Psychology (10.03)

<!-- not yet updated -->

```{r, echo=FALSE}
"https://youtu.be/K3sNg5YbcJA" %>%
 embed_url() %>%
  use_align("center")
```


## Criticisms of Evolutionary Psychology (10.04)

<!-- not yet updated -->

```{r, echo=FALSE}
"https://youtu.be/sm078LdO-CU" %>%
 embed_url() %>%
  use_align("center")
```


# Evolutionary Psych Extras

```{r, echo=FALSE}
include_tweet("https://twitter.com/AdamRutherford/status/1406575489943326721")
```	
