# (PART) Module 11 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
class_urls <- read.csv("./data/class_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Cultural Variation in Experience, Behavior, and Personality

This module is introduces cross-cultural psych. Please watch the videos and work your way through the notes. **The videos start on the next page.**  You can find the module playlist [here](https://www.youtube.com/playlist?list=PLKrrdtYgOUYZ2BXy4ypzoPdA39mszdnlc). 

## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below.

*  Be able to define both cultural and bicultural identity.
*  Know the relationship between behavior, personality, and culture.
*  Understand how the honor, face, and dignity of particular countries contribute to their cultural makeup. cultural makeup.
*  Identify and describe the ways in which culture is studied in psychology.
*  Distinguish between characteristics that are found in all cultures (cultural universals, etics) and traits that are unique to certain cultures (cross-cultural specificity, emics).
*  Identify the different cultural characteristics and understand their implications in cross-cultural psychology.
*  Distinguish between individualist and collectivist cultures.
*  Identify and discuss challenges, controversies, and biases psychologists face when studying personality cross-culturally.
*  Identify and discuss the implications of cultural relativism.
*  Explain the ways in which individuals interact with their culture.
*  Identify the importance of and know the difference between studying both within- and between-culture differences.
*  Define the ecological approach to cross-cultural psychology and understand its implications on cross-cultural psychology.


## Module Materials

### Explore
* Readings
	* Located on Canvas
	* Chapter 13 from the Personality Puzzle
* Videos
  * Located in the subchapters of this module
* Slidedecks
	* Located on Canvas
	
### Engage
* Activities
	* Located on Canvas
	
### Evaluate
* Quiz
	* Located on Canvas



### Estimated Video Length

<!--https://www.youtube.com/playlist?list=PLKrrdtYgOUYao_7t5ycK4KDXNKaY-ECup & https://ytplaylist-len.herokuapp.com/ -->



# Lecture: What is Cross-Cultural Psychology?

## Introduction Cross-Cultural Psychology (11.01)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://youtu.be/5LfJHgMi4Y0") %>%
  use_align("center")
```


## Characteristics of Cultures (11.02)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://youtu.be/SlYG0ZlRP2w") %>%
  use_align("center")
```

## Assessment of Culture and Personality (11.03)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://youtu.be/IwJI-tTI64s") %>%
  use_align("center")
```

## The Origins of Cultural Differences (11.04)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://youtu.be/uHPfUeuxM7g") %>%
  use_align("center")
```

## Challenges and New Directions for Cross-Cultural Research (11.05)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://youtu.be/NfbhWqq0LCE") %>%
  use_align("center")
```
