# (PART) Module 11 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
class_urls <- read.csv("./data/class_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Basics of Psychoanalysis

This module is designed to <TOPIC>. Please watch the videos and work your way through the notes. **The videos start on the next page.**  You can find the module playlist [here](https://www.youtube.com/playlist?list=PLKrrdtYgOUYZ2BXy4ypzoPdA39mszdnlc). 

## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below.

* Know the major tenets of Freud's therapeutic philosophy and technique.
* Identify aspects of Freud's legacy.
* Identify the key ideas behind psychoanalytic theory as well as its overarching goal.
* Explain conventional and unconventional behavior from a psychoanalytic perspective.
* Identify the parts that make up the internal structure of the mind.
* Review criticisms and controversies of psychoanalysis.
* Identify current psychoanalytic therapeutic tendencies.
* Describe the psychosocial stages of development.
* Discuss how individuals move through the psychosocial stages.
* Know the extreme consequences of not successfully moving through each stage in a normative way.
* Define fixation, regression, identification.
* Distinguish between primary and secondary process thinking.
* Identify and discuss the different levels of the topographic model of thinking.
* Discuss how dreams fit in to Freud's model of consciousness.
* Explain how the various parapraxis and defense mechanisms are deterministic.


## Module Materials

### Explore
* Readings
	* Located on Canvas
	* Chapter 10 from the Personality Puzzle
* Videos
  * Located in the subchapters of this module
* Slidedecks
	* Located on Canvas
	
### Engage
* Activities
	* Located on Canvas
	
### Evaluate
* Quiz
	* Located on Canvas



### Estimated Video Length

<!--https://www.youtube.com/playlist?list=PLKrrdtYgOUYao_7t5ycK4KDXNKaY-ECup & https://ytplaylist-len.herokuapp.com/ -->



# What is Module?

## Video 1

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```


## Video 2

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```

## Video 3

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```
