# (PART) Module 13 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
class_urls <- read.csv("./data/class_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Psychoanalysis After Freud

This module covers modern aspects of Psychoanalysis After Freud Please watch the videos and work your way through the notes. **The videos start on the next page.**  You can find the module playlist [here](https://www.youtube.com/playlist?list=PLKrrdtYgOUYZ2BXy4ypzoPdA39mszdnlc). 

## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below.

* Relate the various neo-Freudians with their specific psychoanalytic approach.
* Identify contemporary psychoanalytic theory in general and understand how it relates to the main tenets of classic psychoanalytic theory.
* Understand the common ways Freudian ideas are interpreted today.
* Identify the ways in which neo-Freudians differ from Freud in their approach to psychoanalysis.
* Understand modern neo-Freudians and their theoretical contributions to current research.
* Be able to identify how neo-Freudians explain life-span development.
* Understand the ways in which neo-Freudian ideas have influenced modern personality and developmental and social psychology.
* Identify the major tenets behind object relations theory and how it relates to classic psychoanalytic theory.
* Evaluate contemporary psychological research in relation to classic psychoanalytic theory.
* Identify Freudian theories that have modern scientific support and those that do not.



## Module Materials

### Explore
* Readings
	* Located on Canvas
	* Chapter 11 from the Personality Puzzle
* Videos
  * Located in the subchapters of this module
* Slidedecks
	* Located on Canvas
	
### Engage
* Activities
	* Located on Canvas
	
### Evaluate
* Quiz
	* Located on Canvas



### Estimated Video Length

<!--https://www.youtube.com/playlist?list=PLKrrdtYgOUYao_7t5ycK4KDXNKaY-ECup & https://ytplaylist-len.herokuapp.com/ -->



# Lecture: Psychoanalysis After Freud

## Psychology and Modern Psychoanalysis (13.01)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://youtu.be/1kgz8FWuRfg") %>%
  use_align("center")
```


## Inferiority & Compensation + Feminine Psychology (13.02)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://youtu.be/ExCAR6v9kBo") %>%
  use_align("center")
```

## The Collective Unconscious, Persona, and Personality (13.03)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://youtu.be/FJdQ50XBDqc") %>%
  use_align("center")
```

## Psychosocial Development (13.04)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://youtu.be/UtC2MNk9yZc") %>%
  use_align("center")
```


## Current Psychoanalytic Research (13.05)

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://youtu.be/pBV2Mhmd36s") %>%
  use_align("center")
```


### Discussion of Animal Attachment Research (13.05B)

<!-- not mine -->

```{r, echo=FALSE}
embed_url("https://youtu.be/1zyNbdDgUb8") %>%
  use_align("center")
```


### Illustration of the attachment study paradigm (13.05C)

<!--not mine -->

```{r, echo=FALSE}
embed_url("https://youtu.be/CuIYD-zTEDc") %>%
  use_align("center")
```

## Psychoanalysis in Perspective (13.06)


<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://youtu.be/z2WMGFrkjk4") %>%
  use_align("center")
```

