# (PART) Module 13 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
class_urls <- read.csv("./data/class_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Positive Psychology and the Science of Happiness

This module is designed to <TOPIC>. Please watch the videos and work your way through the notes. **The videos start on the next page.**  You can find the module playlist [here](https://www.youtube.com/playlist?list=PLKrrdtYgOUYZ2BXy4ypzoPdA39mszdnlc). 

## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below.

* 	Be able to identify and explain the central ideas associated with humanistic psychology and phenomenology in general.
* 	Identify the various phenomenology and humanism philosophers and understand how their ideas contribute to our understanding of the human experience.
* 	Understand the central tenets of existentialism and identify the different perspectives from its various philosophers.
* 	Understand the various concepts associated with optimistic humanism and how these ideas enable individuals to reach their optimal selves.
* 	Understand the central tenets of self-determination theory.
* 	Define the positive experiences of mindfulness, flow, and awe, and understand how they relate to other phenomenological concepts.
* 	Understand how the concept of personal constructs enables one to organize the world and how this organization relates to an individual’s construal of the world.
* 	Apply the philosophical concepts associated with humanism and phenomenology to personality and social psychology research and to business and economic practices.
* 	Apply humanistic, existentialistic, and other ideas to the ideas taught by religion.
* 	Relate the ideas put forth in humanistic psychology to various psychoanalytic approaches.
* 	Understand the basic tenets of positive psychology and how they relate to that of humanistic psychology.
* 	Understand happiness and identify what contributes to one's level of happiness.




## Module Materials

### Explore
* Readings
	* Located on Canvas
	* Chapter 12 from the Personality Puzzle
* Videos
  * Located in the subchapters of this module
* Slidedecks
	* Located on Canvas
	
### Engage
* Activities
	* Located on Canvas
	
### Evaluate
* Quiz
	* Located on Canvas



### Estimated Video Length

<!--https://www.youtube.com/playlist?list=PLKrrdtYgOUYao_7t5ycK4KDXNKaY-ECup & https://ytplaylist-len.herokuapp.com/ -->



# Lecture: What is Module?

## Video 1

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```


## Video 2

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```

## Video 3

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```
