# (PART) Module 14 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
class_urls <- read.csv("./data/class_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Personality Processes, Positive Psychology, and the Science of Happiness

This module is designed to understand personality processess as well as positive psychology. Please watch the videos and work your way through the notes. **The videos start on the next page.**  You can find the module playlist [here](https://www.youtube.com/playlist?list=PLKrrdtYgOUYZ2BXy4ypzoPdA39mszdnlc). 

## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below.

### Positive Psychology
* 	Be able to identify and explain the central ideas associated with humanistic psychology and phenomenology in general.
* 	Identify the various phenomenology and humanism philosophers and understand how their ideas contribute to our understanding of the human experience.
* 	Understand the central tenets of existentialism and identify the different perspectives from its various philosophers.
* 	Understand the various concepts associated with optimistic humanism and how these ideas enable individuals to reach their optimal selves.
* 	Understand the central tenets of self-determination theory.
* 	Define the positive experiences of mindfulness, flow, and awe, and understand how they relate to other phenomenological concepts.
* 	Understand how the concept of personal constructs enables one to organize the world and how this organization relates to an individual’s construal of the world.
* 	Apply the philosophical concepts associated with humanism and phenomenology to personality and social psychology research and to business and economic practices.
* 	Apply humanistic, existentialistic, and other ideas to the ideas taught by religion.
* 	Relate the ideas put forth in humanistic psychology to various psychoanalytic approaches.
* 	Understand the basic tenets of positive psychology and how they relate to that of humanistic psychology.
* 	Understand happiness and identify what contributes to one's level of happiness.

### Personality Processes
* 	Identify the basic personality processes and how they act as the mechanisms of personality psychology in general.
* 	Know the underlying cognitive processes behind perception (i.e. priming) and how they inform individual differences.
* 	Differentiate between rejection sensitivity, aggression, and perceptual defense in their behavioral outcomes and relations to personality.
* 	Distinguish between two types of thinking (reflexive vs. impulsive and rational vs. experiential), know the underlying components of each, and understand how each is related to an individual’s personality.
* 	Distinguish between conscious thought and unconscious thought in their capabilities and limitations.
* 	Know the different types of goals and how each acts as a motivating force in an individual’s life.
* 	Know the different strategies individuals use to accomplish their goals and how these strategies relate to their personality, situations, and behavior.
* 	Understand what contributes to one’s emotional experience and the individual differences that underlie these experiences.
* 	Distinguish between the different types of emotions in their consequences, contributing factors, and behavioral outcomes.
* 	Know the historical underpinnings behind the various personality processes.
* 	Identify and describe the different ways to conceptualize goals and personal change and the ways in which these conceptualizations, including the nature of the goals themselves, change over time.



## Module Materials

### Explore
* Readings
	* Located on Canvas
	* Chapter 12 from the Personality Puzzle
* Videos
  * Located in the subchapters of this module
* Slidedecks
	* Located on Canvas
	
### Engage
* Activities
	* Located on Canvas
	
### Evaluate
* Quiz
	* Located on Canvas



### Estimated Video Length

<!--https://www.youtube.com/playlist?list=PLKrrdtYgOUYao_7t5ycK4KDXNKaY-ECup & https://ytplaylist-len.herokuapp.com/ -->



# Lecture: Processes and Positives!

## Introducing Personality Processes and Positive Psychology (14.01)

<!-- not yet updated -->

```{r, echo=FALSE}
"https://youtu.be/d71LYIGtFbk" %>%
 embed_url() %>%
  use_align("center")
```


## The Historical Roots of Personality Processes (14.02)

<!-- not yet updated -->

```{r, echo=FALSE}
"https://youtu.be/vE_AjnSMjZU" %>%
 embed_url() %>%
  use_align("center")
```

## Processes of Perception (14.03)

<!-- not yet updated -->

```{r, echo=FALSE}
"https://youtu.be/AHESbZ9HCrw" %>%
 embed_url() %>%
  use_align("center")
```

## Processes of Thought and Consciousness (14.04)

<!-- not yet updated -->

```{r, echo=FALSE}
"https://youtu.be/PjAQ1WWnr_0" %>%
 embed_url() %>%
  use_align("center")
```

## Ways of Thinking (14.05)

<!-- not yet updated -->

```{r, echo=FALSE}
"https://youtu.be/3xpGtURdlaQ" %>%
 embed_url() %>%
  use_align("center")
```

## Motivation & Goals (14.06)

<!-- not yet updated -->

```{r, echo=FALSE}
"https://youtu.be/gH6DdttMTPw" %>%
 embed_url() %>%
  use_align("center")
```

## Motivation Strategies (14.07)

<!-- not yet updated -->

```{r, echo=FALSE}
"https://www.youtube.com/watch?v=NVAk6DeYMmA" %>%
 embed_url() %>%
  use_align("center")
```

## Emotion (14.08)

<!-- not yet updated -->

```{r, echo=FALSE}
"https://youtu.be/mgid-8XtZDE" %>%
 embed_url() %>%
  use_align("center")
```


## Happiness and Positive Psychology (14.09)

<!-- not yet updated -->

```{r, echo=FALSE}
"https://youtu.be/7hWKaXT_4Vg" %>%
 embed_url() %>%
  use_align("center")
```



