# (PART) Module 16 {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
class_urls <- read.csv("./data/class_urls.csv")
```

```{r links, child="links.md"}
```

# Welcome to Mental and Physical Health

This module is designed to <TOPIC>. Please watch the videos and work your way through the notes. **The videos start on the next page.**  You can find the module playlist [here](https://www.youtube.com/playlist?list=PLKrrdtYgOUYZ2BXy4ypzoPdA39mszdnlc). 

## Learning Goals

By the end of this module, you should be able to achieve all the learning goals outlined below.

*  Understand the purpose, benefits, and criticisms of the Diagnostic and Statistical Manual (DSM).
*  Know the differences between the DSM-IV and DSM-5 and the controversy behind the major changes that took place in writing the new section of the DSM-5.
*  Identify and discuss the defining characteristics of personality disorders.
*  Identify each of the major personality disorders and discuss their severity and prevalence.
*  Be able to identify the behavior and thought patterns associated with each of the six major personality disorders.
*  Understand how the new DSM-5 organizes the major personality disorders and how each relates to the Big Five personality traits.
*  Understand how psychologists collect and evaluate data on health and why it is often difficult.
*  Identify the steps and approaches clinical psychologists take to diagnose patients based on systems laid out by the new DSM-5.
*  Understand the negative consequences diagnoses of the major personality disorders introduces.
*  Identify the various links between personality and health outcomes.
*  Understand the organizations of the old DSM-IV categories.
*  Discuss the concept of the “healthy personality” and routes individuals can take to improve their health.
 



## Module Materials

### Explore
* Readings
	* Located on Canvas
	* Chapter 17 from the Personality Puzzle
* Videos
  * Located in the subchapters of this module
* Slidedecks
	* Located on Canvas
	
### Engage
* Activities
	* Located on Canvas
	
### Evaluate
* Quiz
	* Located on Canvas



### Estimated Video Length

<!--https://www.youtube.com/playlist?list=PLKrrdtYgOUYao_7t5ycK4KDXNKaY-ECup & https://ytplaylist-len.herokuapp.com/ -->



# Lecture: What is Module?

## Video 1

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```


## Video 2

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```

## Video 3

<!-- not yet updated -->

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=4CRRdWGGatQ") %>%
  use_align("center")
```
